### 2017-02-21 thesis/results/results2.tex
tmp commit

Metagene scores used for the construction of linear models were generated from the application of the transformation matrices derived from Gatza's data (from \cref{sec:pathway_associated_metagenes_and_obesity_associated_metagenes}) to \gls{rma}-normalised Cris' data.
For each of the obesity metagenes identified, seven linear models were created: \gls{bmi}-only, \gls{bmi} status-only, \gls{bmi} and \gls{bmi} status, pathway metagenes-only, and all of the combinations of pathway metagenes with \gls{bmi} and/or \gls{bmi} status.

>>>>

Metagene scores used for the construction of linear models were generated from the application of the transformation matrices derived from Gatza's data (from \cref{sec:pathway_associated_metagenes_and_obesity_associated_metagenes}) to \gls{rma}-normalised Cris' data.
For each of the obesity metagenes identified, seven linear models were created: \gls{bmi}-only, \gls{bmi} status-only, \gls{bmi} and \gls{bmi} status, pathway metagenes-only, and all of the combinations of pathway metagenes with \gls{bmi} and/or \gls{bmi} status.
The only variables that showed significance in any of the models that predicted the obesity metagenes taken from the Creighton \textit{et al.} data set were \gls{pr} metagene and whether samples were obese or not (\cref{tab:lm_sig_var}).
In the model that predicted the FM metagene scores, the obesity status of the samples and Myc metagene score were significant, but the \gls{pr} metagene score was not (\cref{app:b}).

\begin{table}[htpb]
	\centering
	\caption{Description of the linear models used to predict the CR obesity metagene}
	\label{tab:lm_sig_var}
	\begin{threeparttable}
		\begin{tabular}{llrr}
			Linear Model & Variables & Estimate & P-value\\
			\hline
			\hline
			\rule{0pt}{2.25ex}\gls{bmi}-only                           & \gls{bmi}  & -0.0016 & 0.717\\
			\hline
			\rule{0pt}{2.25ex}\gls{bmi} status-only                    & Overweight & -0.0126 & 0.871\\
                                                                       & Obese      & -0.0981 & 0.166\\
			\hline
			\rule{0pt}{2.25ex}\gls{bmi} and \gls{bmi} status           & \gls{bmi}  & 0.0109  & 0.123\\
                                                                       & Overweight & -0.0687 & 0.420\\
                                                                       & Obese      & -0.2481 & \textbf{0.040}\tnote{1}\\
			\hline
			\rule{0pt}{2.25ex}Pathways only                            & \gls{bcat} & 0.0916  & 0.677\\
                                                                       & \gls{er}   & 0.0523  & 0.834\\
                                                                       & \gls{ifna} & -0.4993 & 0.307\\
                                                                       & \gls{ifny} & 0.4224  & 0.398\\
                                                                       & Myc        & -0.0038 & 0.987\\
                                                                       & \gls{pr}   & 0.5836  & \textbf{0.016}\\
			\hline
			\rule{0pt}{2.25ex}\gls{bmi} and Pathways                   & \gls{bmi}  & -0.0024 & 0.527\\
                                                                       & \gls{bcat} & 0.1121  & 0.614\\
                                                                       & \gls{er}   & 0.0540  & 0.829\\
                                                                       & \gls{ifna} & -0.5383 & 0.276\\
                                                                       & \gls{ifny} & 0.4661  & 0.358\\
                                                                       & Myc        & 0.0168  & 0.941\\
                                                                       & \gls{pr}   & 0.5927  & \textbf{0.015}\\
			\hline
			\rule{0pt}{2.25ex}\gls{bmi} status and Pathways            & Overweight & -0.0120 & 0.864\\
                                                                       & Obese      & -0.1035 & 0.113\\
                                                                       & \gls{bcat} & 0.1495  & 0.501\\
                                                                       & \gls{er}   & 0.0326  & 0.896\\
                                                                       & \gls{ifna} & -0.6707 & 0.177\\
                                                                       & \gls{ifny} & 0.5888  & 0.245\\
                                                                       & Myc        & 0.0439  & 0.846\\
                                                                       & \gls{pr}   & 0.5799  & \textbf{0.016}\\
			\hline
			\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and pathways & \gls{bmi}  & 0.0091  & 0.161\\
                                                                       & Overweight & -0.0576 & 0.455\\
                                                                       & Obese      & -0.2292 & \textbf{0.040}\\
                                                                       & \gls{bcat} & 0.1460  & 0.509\\
                                                                       & \gls{er}   & 0.0091  & 0.971\\
                                                                       & \gls{ifna} & -0.6937 & 0.161\\
                                                                       & \gls{ifny} & 0.5890  & 0.243\\
                                                                       & Myc        & 0.0263  & 0.907\\
                                                                       & \gls{pr}   & 0.5449  & \textbf{0.024}\\
			\hline
			\hline
		\end{tabular}
		\begin{tablenotes}
			\item [1] All values in bold are statistically significant (p \textless{} 0.05).
		\end{tablenotes}
	\end{threeparttable}
\end{table}

All of the models constructed from sample \gls{bmi}, \gls{bmi} status and/or Gatza's pathway metagene scores confirmed that none of the pathways were significant, except for the \gls{pr} and Myc pathway metagene scores in the models for Creighton metagenes and FM metagene, respectively.
It was not surprising that the \gls{pr} pathway metagene showed significance in the models generated in Cris' data set, as \gls{pr} status was very strongly correlated with Cris' data set.
The significance of the Myc metagene in the model for FM metagene was difficult to interpret, as there was no reported association of FM metagene with Myc pathway by \citet{Fuentes-Mattei2014}.
However, ``sustained cell proliferation'' was one of the cancer hallmarks that \citet{Fuentes-Mattei2014} had shown to be related to their obesity genetic signature, so the Myc pathway metagene may have picked up the proliferation signal in the FM metagene.

Since the \gls{pr} pathway metagene showed significant association in many of the linear models, linear models were made with all of the combinations of \gls{bmi}, \gls{bmi} status and \gls{pr} pathway metagene for all of the obesity associated metagenes (\cref{tab:lm_pr_only} and \cref{app:b}).

\begin{table}[htpb]
	\centering
	\caption{Description of the linear models used to predict the CR obesity metagene, using only the sample \gls{bmi}, \gls{bmi} status and \gls{pr} pathway metagene scores}
	\label{tab:lm_pr_only}
	\begin{threeparttable}
			\begin{tabular}{llrS[detect-weight]}
				Linear Model & Variables & Estimate &P-value\\
				\hline
				\hline
				\rule{0pt}{2.25ex}\gls{pr}-only & \gls{pr}   & 0.477  & {\num{6.06d-7}}\tnote{1}\\
			\end{tabular}
			\begin{tablenotes}
				\item [1] All values in bold are statistically significant (p \textless{} 0.05).
			\end{tablenotes}
	\end{threeparttable}
\end{table}
% \begin{table}[htpb]
% 	\centering
% 	\caption{Description of the linear models used to predict the CR obesity metagene, using only the sample \gls{bmi}, \gls{bmi} status and \gls{pr} pathway metagene scores}
% 	\label{tab:lm_pr_only}
% 	\begin{threeparttable}
% 			\begin{tabular}{llrS}
% 				Linear Model & Variables & Estimate &P-value\\
% 				\hline
% 				\hline
% 				\rule{0pt}{2.25ex}\gls{pr}-only                            & \gls{pr}   & 0.477  & \num{6.06d-7}\tnote{1}\\
% 				\hline
% 				\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.002 & 0.586\\
%                                                                            & \gls{pr}   & 0.478  & 6.35 \times10^{-7}\\
% 				\hline
% 				\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.085 & 0.176\\
%                                                                            & Overweight & -0.011 & 0.875\\
%                                                                            & \gls{pr}   & 0.471  & 8.25 \times10^{-7}\\
% 				\hline
% 				\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.007  & 0.237\\
%                                                                            & Obese      & -0.188 & 0.081\\
%                                                                            & Overweight & -0.049 & 0.516\\
%                                                                            & \gls{pr}   & 0.459  & 1.54 \times10^{-6}\\
% 				\hline
% 				\hline
% 			\end{tabular}
% 			\begin{tablenotes}
% 				\item [1] All values in bold are statistically significant (p \textless{} 0.05).
% 			\end{tablenotes}
% 	\end{threeparttable}
% \end{table}

### 2017-02-21 thesis/thesis.tex
tmp commit
tmp commit; added appendix file
Added figure images into results; tmp commit
finished pathway and obesity metagene section - tmp commit

% Preamble:
\usepackage[T1]{fontenc}                               % package for specifying output font encoding
\usepackage[utf8]{inputenc}                            % package for specifying input font encoding
\usepackage{natbib}                                    % package for reference management
\usepackage{graphicx}                                  % package for graphics handling (i.e. figure images)
\usepackage{mathptmx}                                  % package for Times New Roman font
\usepackage{chngcntr}                                  % package for making continuous figure numbering, instead of section-based numbering
\usepackage[flushleft]{threeparttable}                 % package to add notes at the bottom of the table
\usepackage{setspace}                                  % package for setting line space (used in title page)
\usepackage[hidelinks, colorlinks]{hyperref}           % package for hyperlinking references - hidelinks option removes the ugly boxes around the huperlinks
\usepackage[md]{titlesec}                              % package for tweaking the chapter/section/subsection titles format
\usepackage[acronym]{glossaries} % package for making glossaries
\usepackage{xcolor,colortbl}                           % package for making colours
\usepackage[noabbrev,capitalise]{cleveref}             % package for referencing multiple referencing in a single \ref command
\usepackage[font=footnotesize,format=hang]{caption}    % package for formatting figure caption
\usepackage{subcaption}    % package for formatting figure caption

@@

@@

% If you want to compile specific files, uncomment the line below and add the filenames in the {} :
\includeonly{./results/results}

@@

>>>>

% Preamble:
\usepackage[T1]{fontenc}                            % package for specifying output font encoding
\usepackage[acronym]{glossaries}                    % package for making glossaries
\usepackage[flushleft]{threeparttable}              % package to add notes at the bottom of the table
\usepackage[font=footnotesize,format=hang]{caption} % package for formatting figure caption
\usepackage[hidelinks, colorlinks]{hyperref}        % package for hyperlinking references - hidelinks option removes the ugly boxes around the huperlinks
\usepackage[md]{titlesec}                           % package for tweaking the chapter/section/subsection titles format
\usepackage[noabbrev,capitalise]{cleveref}          % package for referencing multiple referencing in a single \ref command
\usepackage[toc]{appendix}                          % package for making appendices
\usepackage[utf8]{inputenc}                         % package for specifying input font encoding
\usepackage{chngcntr}                               % package for making continuous figure numbering, instead of section-based numbering
\usepackage{graphicx}                               % package for graphics handling (i.e. figure images)
\usepackage{mathptmx}                               % package for Times New Roman font
\usepackage{natbib}                                 % package for reference management
\usepackage{setspace}                               % package for setting line space (used in title page)
\usepackage{xcolor,colortbl}                        % package for making colours
\usepackage{booktabs}                               % package for better looking tables
\usepackage{longtable}                              % package for tables that span multiple pages
\usepackage{siunitx}                                % package for scientific notations and units
\usepackage{bm}                                % package for scientific notations and units

@@

% Change the default cref name for appendix:
\crefname{appcha}{Appendix}{Appendices}
\crefname{appsec}{Appendix}{Appendices}

% Make siunitx detect bold/italics/etc:
\sisetup{detect-weight=true,detect-family=true,detect-inline-weight=text,table-parse-only}

@@

% If you want to compile specific files, uncomment the line below and add the filenames in the {} :
\includeonly{{./methods/methods},{./results/results},{./results/results2},{./misc/appendix}}
% \includeonly{{./results/results},{./results/results2},{./misc/appendix}}

@@

\include{./misc/appendix}
